Python_basic

### 2022-11-03 Python_basic.qmd
The First steps with Selenium.

```{r}
library(reticulate)
py_install("bs4", method="conda" )
py_install("pandas", method="conda" )

@@

>>>>

```{r}
library(reticulate)
py_install("bs4", method="conda" )
py_install("pandas", method="conda" )
py_install("selenium", method="conda" )

@@

```{python}
#| label: Selenium installation with Chrome Webdriver

# Source: https://www.youtube.com/watch?v=pUUhvJvs-R4

from selenium import webdriver
from selenium.webdriver.common.keys import Keys

drv_path = "C:\\Users\\I0172484\\Documents\WebDriver\\chromedriver.exe"
driver = webdriver.Chrome(drv_path)

url="http://the-internet.herokuapp.com/login"
driver.get(url)

driver.find_element("xpath", '//*[@id="username"]').send_keys('tomsmith')
driver.find_element("xpath", '//*[@id="password"]').send_keys('SuperSecretPassword!')
driver.find_element("xpath", '//*[@id="login"]/button').click()
